---
title: 'Clean insect visitors dataset'
author: "B. Karina Montero "
date: "`r Sys.Date()`"
output: rmarkdown::github_document
---


### LOAD LIBRARIES

```{r libraries, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

rm(list = ls())

# basics
library(tidyverse)
library(stringr)
library(vegan)
library(magrittr)
library(ggplot2)
library(ggpubr)

# diversity 
#install.packages("iNEXT")
library("iNEXT")
library(hilldiv)

# rmd
library(details)
library(knitr)
library(kableExtra)
```

### WORKING DIRECTORIES

```{r source, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, results="hide"}

source("/home/kari/Dropbox/PollenUCR/01_scripts/UCR_workingDirectories.R")

```

### LOAD DATA

```{r metadata, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

bichos <- read.csv(paste0(dataDir, "/Base_unificada.csv"))

#remove messy columns
bichos <- bichos[, -c(35:45)] 

# Figure out sampling unit
bichos$Proj_site <- paste(bichos$Project, bichos$Fruitcrop_transect, sep = "_")

bichos$Sampling_unit <- paste(bichos$Project, bichos$Sampling_session, bichos$Fruitcrop_transect,  bichos$Month, sep = "_")

bichos$Sampling_unit[1:3]

check_sampling <- as.data.frame(table(bichos$Sampling_unit))
names(check_sampling) <- c("Sampling_unit", "n_visitors") 

n_plants_sampling <- bichos %>% 
						group_by(Sampling_unit) %>% 
						summarise(n_plants = n_distinct(Tree_code))
						
check_sampling <- left_join(check_sampling, n_plants_sampling, by = "Sampling_unit")

head(check_sampling)

bichos$Proj_season <- paste(bichos$Project, bichos$Season, sep = "_")

(sample_size_project <- bichos %>%
 							group_by(Project) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit))) 

(sample_size_fruitcrop <- bichos %>%
 							group_by(Fruitcrop_transect) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit))) 

(sample_size_sampling <- bichos %>%
 							group_by(Proj_site) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit))) 
sum(sample_size_sampling$n_sampling)

(sample_size_farm <- bichos %>%
 							group_by(Proj_site, Farm_transect) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit))) 

(sample_size_crop <- bichos %>%
							filter(Project == "Cultivos") %>%
 							group_by(Plant_species) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit))) 

(sample_size_proj_season <- bichos %>%
 							group_by(Proj_season) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit))) 


# add rownames to dataframe
rownames(bichos) <- bichos$ID_code_unique

# check data
nrow(bichos)

table(bichos$Project)
table(bichos$Fruitcrop_transect)
table(bichos$Collected_or_sighting)
table(bichos$Project, bichos$Collected_or_sighting)

giras <- read.csv(paste0(dataDir, "/Datos_giras.csv"))

# Figure out sampling unit
giras$Proj_site <- paste(giras$Project, giras$Fruitcrop_transect, sep = "_")

giras$Sampling_unit <- paste(giras$Project, giras$Sampling_session, giras$Fruitcrop_transect, giras$Day, giras$Month, sep = "_")

(summary_farms <- giras %>% group_by(Farm_transect, Fruitcrop_transect, ) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit)) %>% data.frame) 

(summary_giras <- giras %>% filter(Project == "Cultivos") %>%
 							group_by(Month_num, Plant_species) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit)) %>% data.frame)

days_per_sampling <- giras %>% 
 							group_by(Project, Sampling_session) %>% 
 							summarise(days_per_sampling = n_distinct(Day)) %>% data.frame  
(total_hours_project <- giras %>% 
					group_by(Project, Sampling_unit) %>%
					summarise(hours_per_sampling = min(Sampling_hours)) %>%
					group_by(Project)%>%
					summarise(total_hours = sum(hours_per_sampling)) %>%	data.frame
)

(total_hours_plant_transect <- giras %>% 
					group_by(Fruitcrop_transect, Sampling_unit) %>%
					summarise(hours_per_sampling = min(Sampling_hours)) %>%
					group_by(Fruitcrop_transect)%>%
					summarise(total_hours = sum(hours_per_sampling)) %>%	
					 data.frame
)

giras_to_merge <- giras %>% 
 							group_by(Project, Sampling_session, Fruitcrop_transect, Day) %>%
 							summarise(giras_to_merge = n_distinct(paste(Sampling_session, Day))) %>% data.frame  

giras_subset <- giras %>% select(Project, Sampling_session, Day, Fruitcrop_transect, Sampling_hours) %>% distinct()

giras_to_merge <- right_join(giras_to_merge, giras_subset, by = c("Project" , "Sampling_session", "Fruitcrop_transect", "Day" ))
str(giras_to_merge)

```

### CLEAN TAXONOMY

```{r exploreTax, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

tax <- bichos %>% select(Order, Family, Genus, Species, Lowest_assignment) 

tax[is.na(tax)] <- "NA"
str(tax)

table(tax$Order)

# num Families minus 1 (NA)
nrow(data.frame(table(tax$Family))) -1

# num Genera minus 1 (NA)
nrow(data.frame(table(tax$Genus))) -1

# Explore unsassigned 
family_na <- tax %>% filter(Family == "NA") 

# num of specimens unassigned to Family level
nrow(family_na)

table(family_na$Order)

```

Remove individuals that did not get assigned to Family level and hummingbirds.

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

tax_filter <- tax %>% filter(Family != "NA" & Order != "Apodiformes") 
str(tax_filter)

tax_filter %>%
		summarise(n_Order = n_distinct(Order), 
				n_Family = n_distinct(Family), 
				n_Genus = n_distinct(Genus), 
				n_Lowest = n_distinct(Lowest_assignment), 
				n_species = n_distinct(Species)) 

```

Explore unassigned Genera

```{r exploreGenus, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

# num of individuals unassigned to Genus level

genus_na <- tax %>% filter(Family != "NA", Genus == "NA") 
nrow(genus_na)

# Perc of individuals unnasigned to Genus
(799/4112)*100

count_genus_na <- as.data.frame(table(genus_na$Family))
count_genus_na$Perc_na <- (count_genus_na$Freq/799)*100
count_genus_na$Perc_total <- (count_genus_na$Freq/4112)*100

head(count_genus_na)

(top_unassigned <- count_genus_na %>% filter(Perc_na > 3))

sum(top_unassigned$Perc_total)

```

Explore unassigned Lowest assignment (Species / Morphospecies)


```{r exploreSp, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

# num of specimens unassigned to Genus level
lowest_na <- tax %>% filter(Family != "NA", Lowest_assignment == "NA") 
nrow(lowest_na)

# Perc of specimens unnasigned to Genus
(1064/4112)*100

count_lowest_na <- as.data.frame(table(lowest_na$Genus))
count_lowest_na$Perc_na <- (count_lowest_na$Freq/1064)*100
count_lowest_na$Perc_total <- (count_lowest_na$Freq/4112)*100

head(count_lowest_na, 3)

(top_unassigned <- count_lowest_na %>% filter(Perc_na > 10))

sum(top_unassigned$Perc_total)



```

Replace NA with highest taxonomic assinment

```{r cleanTax, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

for (i in 1:nrow(tax_filter)){
    if (tax_filter[i,2] == "NA"){
    order <- paste("Order_", tax_filter[i,1], sep = "")
    tax_filter[i, 2:4] <- order
    } else if (tax_filter[i,3] == "NA"){
   family <- paste("Family_", tax_filter[i,2], sep = "")
    tax_filter[i, 3:4] <- family
    } else if ((tax_filter[i,4] == "NA")){
    tax_filter$Lowest_assignment[i] <- paste("Genus_", tax_filter[i,2], sep = "")
} else if (tax_filter[i,4] == "NA"){
}
}

head(tax_filter, 3)
tail(tax_filter, 3)

# merge with df
bichos_long <- bichos %>% select(Project, Sampling_session, Sampling_unit, Day, Month, Year, Season, Proj_site, Proj_season, Farm_transect, Fruitcrop_transect, Plant_species)

head(rownames(bichos_long))
head(rownames(tax_filter))

bichos_long <- merge(bichos_long, tax_filter, by = 0, all.x = FALSE) 
names(bichos_long)

sampling_lowest <- bichos_long %>% 
					group_by(Sampling_unit) %>%
					summarise(count_lowest = n_distinct(Lowest_assignment)) %>%
					data.frame

head(sampling_lowest)
head(check_sampling)
check_sampling$Sampling_unit <- as.character(check_sampling$Sampling_unit)

check_sampling_df <- left_join(sampling_lowest, check_sampling, by = "Sampling_unit")
check_sampling_df <- check_sampling_df[order(check_sampling_df$n_plants, check_sampling_df$n_visitors),]
head(check_sampling_df, 12)

#write.csv(check_sampling_df, paste0(dataDir, "/check_sampling_df.csv"))

```

### MERGE AND FILTER

Merge insect data with sampling session info.

```{r merge, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

# add counts to df
bichos_long <- left_join(bichos_long, check_sampling_df, by = "Sampling_unit")

# add sampling hours to df
bichos_long <- left_join(bichos_long, giras_to_merge, by = c("Project", "Sampling_session", "Day", "Fruitcrop_transect" ), keep = FALSE)

Sampling_hours_total <- bichos_long %>% 
				group_by(Project, Sampling_unit) %>%
				distinct(Sampling_hours) %>%
				arrange(Sampling_unit) %>%
				mutate(Sampling_hours_total = sum(Sampling_hours)) %>%
				select(-Sampling_hours) %>% 
				distinct(Sampling_unit, Sampling_hours_total) %>%
				data.frame


bichos_long <- right_join(bichos_long, Sampling_hours_total, by = c("Sampling_unit", "Project"))

check_sampling_df_2 <- bichos_long %>%
					distinct(Sampling_unit, count_lowest, n_visitors, n_plants, Sampling_hours_total) %>% arrange(Sampling_hours_total)
head(check_sampling_df_2, 15)

write.csv(check_sampling_df_2, paste0(dataDir, "/check_sampling_fadf.csv"))

```

Remove sampling sessions with very low sampling effort (< 2hours)


```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

# n sampling units before filtering 
bichos_long %>% group_by(Fruitcrop_transect) %>%
					summarise(n_distinct(Sampling_unit))

# remove sampling units with very low sampling effort
bichos_long_filter <- bichos_long %>% filter(Sampling_hours_total  >= 2 )

# n sampling units after filtering
bichos_long_filter %>% group_by(Fruitcrop_transect) %>%
						summarise( n_distinct(Sampling_unit))
bichos_long_filter %>% group_by(Project) %>%
						summarise( n_distinct(Sampling_unit))						

(total_hours_project <- bichos_long_filter %>% 
					group_by(Project, Sampling_unit)%>%
					distinct(Sampling_hours_total) %>%
					group_by(Project) %>%
					summarise(total_hours = sum(Sampling_hours_total)) %>%	data.frame
)
136.65 + 97.25

```

Supplementary Tables

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

y <- c("Persea americana","Rubus","Malus domestica","Prunus domestica", "Suria", "Tajo")

oldnames <- c("August", "July", "September", "December", "June", "November", "October", "January", "February", "May",  "April", "March")
newnames <- c("Aug", "Jul", "Sep", "Dec", "Jun", "Nov", "Oct", "Jan", "Feb", "May",  "Apr", "Mar")


(sample_size_month <- bichos_long_filter %>% 
							group_by(Year, Fruitcrop_transect, Month) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit)) %>% 
 							pivot_wider(names_from = Month, values_from = n_sampling, values_fill = 0) %>%
 							arrange(match(Fruitcrop_transect, y)) %>%
 							data.frame %>% 
 							rename_at(all_of(oldnames), ~ newnames) %>%
 							select(Year, Fruitcrop_transect, Jan, Feb, Mar, Apr, May, Jun, Jul, Aug, Sep, Oct, Nov, Dec ))

silvestres_info <- read.csv(paste0(dataDir, "/silvestres_info.csv"))
head(silvestres_info)

bichos_long_filter <- left_join(bichos_long_filter, silvestres_info, by = "Plant_species")
names(bichos_long_filter )

flowering_transects <- bichos_long_filter %>%
							filter(Project == "Silvestres") %>%
							group_by(Plant_Family, Plant_species, Month) %>%
							summarise(n_sampling = n_distinct(Sampling_unit)) %>% 			
							pivot_wider(names_from = Month, values_from = n_sampling, values_fill = 0) %>%
							data.frame %>% 
 							rename_at(all_of(oldnames), ~ newnames) %>%
 							select(Plant_Family, Plant_species, Jan, Feb, Mar, Apr, May, Jun, Jul, Aug, Sep, Oct, Nov, Dec)
flowering_transects <- left_join(flowering_transects, silvestres_info, by = c("Plant_Family", "Plant_species"))

write.csv(flowering_transects, paste0(dataDir, "/flowering_transects.csv"), row.names = FALSE)

names(bichos_long_filter)
table(bichos_long_filter$Order)

tax_summary <- bichos_long_filter %>%
							group_by(Order, Family, Genus, Lowest_assignment) %>%
							mutate(
								Genus = ifelse(str_starts(Genus, "Family_"), NA, Genus),
								Lowest_assignment = ifelse(str_starts(Lowest_assignment, "Family_"), NA, Lowest_assignment)) %>% 
							group_by(Order, Family, Genus) %>%
							summarise(
								count_lowest = n_distinct(Lowest_assignment, na.rm = TRUE), 
								abundance = n()) %>%
							data.frame

table(tax_summary$Order)

tax_summary_coleoptera <- tax_summary %>% 
							filter(Order == "Coleoptera")

tax_summary_diptera <- tax_summary %>% 
							filter(Order == "Diptera")

tax_summary_hemiptera <- tax_summary %>% 
							filter(Order == "Hemiptera")

tax_summary_hymenoptera <- tax_summary %>% 
							filter(Order == "Hymenoptera")

tax_summary_lepidoptera <- tax_summary %>% 
							filter(Order == "Lepidoptera")

write.csv(tax_summary_coleoptera, paste0(outputDir, "/list_coleoptera.csv"), row.names = FALSE)
write.csv(tax_summary_diptera, paste0(outputDir, "/list_diptera.csv"), row.names = FALSE)
write.csv(tax_summary_hemiptera, paste0(outputDir, "/list_hemiptera.csv"), row.names = FALSE)
write.csv(tax_summary_hymenoptera, paste0(outputDir, "/list_hymenoptera.csv"), row.names = FALSE)
write.csv(tax_summary_lepidoptera, paste0(outputDir, "/list_lepidoptera.csv"), row.names = FALSE)

```


### OUTPUT FILES

Save clean data files for diversity analyses

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

write.csv(bichos_long, paste0(dataDir,"/bichos_long.csv"))
write.csv(bichos_long_filter, paste0(dataDir,"/bichos_long_filter.csv"))

```

## Session Info

```{r sessionInfo, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}
sessioninfo::session_info()%>%
  details::details(summary = 'Current session info', open = FALSE)
```