---
title: 'Import Reference Database into QIIME2'
author: "B. Karina Montero"
date: "`r Sys.Date()`"
#output: pdf_document
output: html_document
---

B. Karina Montero


## 1. LOAD CRABS AND SPECIFY PATHS

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, results="hide"}

conda activate qiime2-2023.2

cd /home/kari/Dropbox/PollenUCR/01_scripts/RefDB/DB_update


 ```


### 2. IMPORT DATA INTO QIIME2

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, results="hide"}

#DB1_no_derep
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path DB_NCBI_Paramo_merge_km_2023_11_20.fasta \
  --output-path DB_NCBI_Paramo_merge_km_2023_11_20.fasta.qza

 qiime tools import \
  --type 'FeatureData[Taxonomy]' \
  --input-format HeaderlessTSVTaxonomyFormat \
  --input-path NCBI_Paramo_taxonomic_lineages_2023_11_20.tsv \
  --output-path NCBI_Paramo_taxonomic_lineages_2023_11_20.qza

#DB2_derep
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path DB_NCBI_Paramo_merge_derep_km_2023_11_20.fasta \
  --output-path DB_NCBI_Paramo_merge_derep_km_2023_11_20.fasta.qza

qiime tools import \
  --type 'FeatureData[Taxonomy]' \
  --input-format HeaderlessTSVTaxonomyFormat \
  --input-path NCBI_Paramo_taxonomic_lineages_derep_2023_11_20.tsv \
  --output-path NCBI_Paramo_taxonomic_lineages_derep_2023_11_20.qza

#DB3_geoRestricted_no_derep
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path DB_NCBI_Paramo_geoRestricted_merge_km_2023_11_20.fasta \
  --output-path DB_NCBI_Paramo_geoRestricted_merge_km_2023_11_20.fasta.qza

qiime tools import \
  --type 'FeatureData[Taxonomy]' \
  --input-format HeaderlessTSVTaxonomyFormat \
  --input-path DB_NCBI_Paramo_geoRestricted_taxonomic_lineages_2023_11_20.tsv \
  --output-path DB_NCBI_Paramo_geoRestricted_taxonomic_lineages_2023_11_20.qza

#DB4_geoRestricted_derep
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path DB_NCBI_Paramo_geoRestricted_merge_derep_km_2023_11_20.fasta \
  --output-path DB_NCBI_Paramo_geoRestricted_merge_derep_km_2023_11_20.fasta.qza

qiime tools import \
  --type 'FeatureData[Taxonomy]' \
  --input-format HeaderlessTSVTaxonomyFormat \
  --input-path DB_NCBI_Paramo_geoRestricted_derep_taxonomic_lineages_2023_11_20.tsv \
  --output-path DB_NCBI_Paramo_geoRestricted_derep_taxonomic_lineages_2023_11_20.qza

#DB5_no_derep_extract
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path DB_NCBI_Paramo_merge_km_2023_11_20_extract_pga.fasta \
  --output-path DB_NCBI_Paramo_merge_km_2023_11_20_extract_pga.fasta.qza

#DB6_derep_extract
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path DB_NCBI_Paramo_merge_derep_km_2023_11_20_extract_pga.fasta \
  --output-path DB_NCBI_Paramo_merge_derep_km_2023_11_20_extract_pga.fasta.qza

#DB7_geoRestricted_no_derep_extract
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path DB_NCBI_Paramo_geoRestricted_merge_km_2023_11_20_extract_pga.fasta \
  --output-path DB_NCBI_Paramo_geoRestricted_merge_km_2023_11_20_extract_pga.fasta.qza

#DB8_geoRestricted_derep_extract
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path DB_NCBI_Paramo_geoRestricted_merge_derep_km_2023_11_20_extract_pga.fasta \
  --output-path DB_NCBI_Paramo_geoRestricted_merge_derep_km_2023_11_20_extract_pga.fasta.qza

#DB9_no_derep_without_local
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path NCBI_ITS2_Viridiplantae_2023_03_16_clean.fasta \
  --output-path NCBI_ITS2_Viridiplantae_2023_03_16_clean.fasta.qza

qiime tools import \
  --type 'FeatureData[Taxonomy]' \
  --input-format HeaderlessTSVTaxonomyFormat \
  --input-path NCBI_ITS2_Viridiplantae_taxonomic_lineages_2023_03_09.tsv \
  --output-path NCBI_ITS2_Viridiplantae_taxonomic_lineages_2023_03_09.qza

#DB10_derep_without_local
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path NCBI_ITS2_Viridiplantae_2023_03_16_derep_clean.fasta \
  --output-path NCBI_ITS2_Viridiplantae_2023_03_16_derep_clean.fasta.qza

qiime tools import \
  --type 'FeatureData[Taxonomy]' \
  --input-format HeaderlessTSVTaxonomyFormat \
  --input-path NCBI_ITS2_Viridiplantae_taxonomic_lineages_2023_03_09_derep.tsv \
  --output-path NCBI_ITS2_Viridiplantae_taxonomic_lineages_2023_03_09_derep.qza

#DB11_no_derep_geoRestricted_without_local
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path NCBI_ITS2_Viridiplantae_geoRestricted_fasta_file_2023_05_10.fasta \
  --output-path NCBI_ITS2_Viridiplantae_geoRestricted_fasta_file_2023_05_10.fasta.qza

#DB12_derep__geoRestricted_without_local
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path NCBI_ITS2_Viridiplantae_geoRestricted_derep_fasta_file_2023_05_10.fasta \
  --output-path NCBI_ITS2_Viridiplantae_geoRestricted_derep_fasta_file_2023_05_10.fasta.qza

#DB13_no_derep_without_local_extract
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path NCBI_ITS2_Viridiplantae_2023_11_20_extract_pga.fasta \
  --output-path NCBI_ITS2_Viridiplantae_2023_11_20_extract_pga.fasta.qza

#DB14_derep_without_local_extract
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path NCBI_ITS2_Viridiplantae_derep_2023_11_20_extract_pga.fasta \
  --output-path NCBI_ITS2_Viridiplantae_derep_2023_11_20_extract_pga.fasta.qza

#DB15_no_derep_geoRestricted_without_local_extract
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path NCBI_ITS2_Viridiplantae_geoRestricted_2023_11_20_extract_pga.fasta \
  --output-path NCBI_ITS2_Viridiplantae_geoRestricted_2023_11_20_extract_pga.fasta.qza

#DB16_derep_geoRestricted_without_local_extract
qiime tools import \
  --type 'FeatureData[Sequence]' \
  --input-path NCBI_ITS2_Viridiplantae_geoRestricted_derep_2023_11_20_extract_pga.fasta \
  --output-path NCBI_ITS2_Viridiplantae_geoRestricted_derep_2023_11_20_extract_pga.fasta.qza

```


These two files can be directly used in QIIME2 as reference files to assign taxonomy to query sequences using the BLAST+ consensus classifier or the VSEARCH-based consensus classifier.

If the sklearn-based Naive Bayes approach is preferred to assign taxonomy, the classifier must be pre-trained:

Big Job, send to CESGA

## Copy files to cesga

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, results="hide"}


#DB1_no_derep
rsync -ravzhP -v DB_NCBI_Paramo_merge_km_2023_11_20.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

rsync -ravzhP -v NCBI_Paramo_taxonomic_lineages_2023_11_20.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB2_derep
rsync -ravzhP -v DB_NCBI_Paramo_merge_derep_km_2023_11_20.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

rsync -ravzhP -v NCBI_Paramo_taxonomic_lineages_derep_2023_11_20.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB3_geoRestricted_no_derep
rsync -ravzhP -v DB_NCBI_Paramo_geoRestricted_merge_km_2023_11_20.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

rsync -ravzhP -v DB_NCBI_Paramo_geoRestricted_taxonomic_lineages_2023_11_20.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB4_geoRestricted_derep
rsync -ravzhP -v DB_NCBI_Paramo_geoRestricted_merge_derep_km_2023_11_20.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

rsync -ravzhP -v DB_NCBI_Paramo_geoRestricted_derep_taxonomic_lineages_2023_11_20.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB5_no_derep_extract
rsync -ravzhP -v DB_NCBI_Paramo_merge_km_2023_11_20_extract_pga.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB6_derep_extract
rsync -ravzhP -v DB_NCBI_Paramo_merge_derep_km_2023_11_20_extract_pga.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB7_geoRestricted_no_derep_extract
rsync -ravzhP -v DB_NCBI_Paramo_geoRestricted_merge_km_2023_11_20_extract_pga.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB8_geoRestricted_no_derep_extract
rsync -ravzhP -v DB_NCBI_Paramo_geoRestricted_merge_derep_km_2023_11_20_extract_pga.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP


#DB9_no_derep_without_local
rsync -ravzhP -v NCBI_ITS2_Viridiplantae_2023_03_16_clean.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

rsync -ravzhP -v NCBI_ITS2_Viridiplantae_taxonomic_lineages_2023_03_09.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB10_derep_without_local
rsync -ravzhP -v NCBI_ITS2_Viridiplantae_2023_03_16_derep_clean.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

rsync -ravzhP -v NCBI_ITS2_Viridiplantae_taxonomic_lineages_2023_03_09_derep.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB11_no_derep_geoRestricted_without_local
rsync -ravzhP -v NCBI_ITS2_Viridiplantae_geoRestricted_fasta_file_2023_05_10.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB12_derep__geoRestricted_without_local
rsync -ravzhP -v NCBI_ITS2_Viridiplantae_geoRestricted_derep_fasta_file_2023_05_10.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB13_no_derep_without_local_extract
rsync -ravzhP -v NCBI_ITS2_Viridiplantae_2023_11_20_extract_pga.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB14_derep_without_local_extract
rsync -ravzhP -v NCBI_ITS2_Viridiplantae_derep_2023_11_20_extract_pga.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB15_no_derep_geoRestricted_without_local_extract
rsync -ravzhP -v NCBI_ITS2_Viridiplantae_geoRestricted_2023_11_20_extract_pga.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP

#DB16_derep_geoRestricted_without_local_extract
rsync -ravzhP -v NCBI_ITS2_Viridiplantae_geoRestricted_derep_2023_11_20_extract_pga.fasta.qza csddepla@ft3.cesga.es:/mnt/lustre/scratch/nlsas/home/csic/dde/pla/FringillaProject/TEMP


```

## Pre-train classifiers

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, results="hide"}


# depending on the size of the reference database this can be done locally. Takes between 5min to 3.5 hours to run in the cluster 

sbatch classifier_ITS2_1_no_derep.sh
# Run time 
sbatch classifier_ITS2_2_derep.sh
# Run time 
sbatch classifier_ITS2_3_geoRestricted.sh
# Run time 
sbatch classifier_ITS2_4_geoRestricted_derep.sh
# Run time 
sbatch classifier_ITS2_5_extracted.sh
# Run time 
sbatch classifier_ITS2_6_derep_extracted.sh
# Run time 
sbatch classifier_ITS2_7_geoRestricted_extracted.sh
# Run time 
sbatch classifier_ITS2_8_geoRestricted_derep_extracted.sh

sbatch classifier_ITS2_9_no_derep.sh
# Run time 
sbatch classifier_ITS2_10_derep.sh
# Run time 
sbatch classifier_ITS2_11_geoRestricted.sh
# Run time 
sbatch classifier_ITS2_12_geoRestricted_derep.sh
# Run time 
sbatch classifier_ITS2_13_extracted.sh
# Run time 
sbatch classifier_ITS2_14_derep_extracted.sh
# Run time 
sbatch classifier_ITS2_15_geoRestricted_extracted.sh
# Run time 
sbatch classifier_ITS2_16_geoRestricted_derep_extracted.sh

```
