---
title: 'Beta diversity of insect visitors'
author: "B. Karina Montero "
date: "`r Sys.Date()`"
output: html_document
---


### LOAD LIBRARIES

```{r libraries, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

rm(list = ls())

# basics
library(tidyverse)
library(stringr)
library(vegan)
library(magrittr)
library(ggplot2)
library(ggpubr)

# diversity 
library(iNEXT)
library(hilldiv)

# rmd
library(details)
library(knitr)
library(kableExtra)

```

### WORKING DIRECTORIES

```{r source, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, results="hide"}

source("/home/kari/Dropbox/PollenUCR/01_scripts/UCR_workingDirectories.R")

```

### LOAD DATA

```{r metadata, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, results = "hide"}

bichos_long_filter <- read.csv(paste0(dataDir, "/bichos_long_filter.csv"))

```

### GRAPHICAL PARAMETERS
```{r graphParams, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

ord_theme <- theme_set(theme_bw(base_size = 13)) + theme( panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border=element_rect(fill = NA, colour = "black"),plot.margin=grid::unit(c(5,5,5,5), "mm"), axis.text.x = element_text(colour = "black", size=rel(1)), axis.text.y=element_text(size=rel(1), colour="black"), axis.title = element_text(size = rel(1)))

season_order <- c("dry", "rainy")

season_col <- c("#FFC107", "#004D40")

season_color <- scale_color_manual(name = "Season",
                                   values = season_col,
                                   limits = season_order,
                                   labels = c("Dry", "Wet")
                                   #guide = "right"
                                   )
season_fill <- scale_fill_manual(name = "Season",
                                   values = season_col,
                                   limits = season_order,
                                   labels = c("Dry", "Wet")
                                   #guide = "none"
                                   )

project_order <- c("Cultivos", "Silvestres")

project_symbol <- c(21, 22)

project_line <- c(1, 2)

project_shape <- scale_shape_manual(name = "Sampling",
                                   values = project_symbol,
                                   limits = project_order,
                                   labels = c("Fruit crops", "Wild plants")
                                   #guide = "right"
                                   )


project_line <- scale_linetype_manual(name = "",
                                   values = project_line,
                                   limits = project_order,
                                   labels = c("Fruit crops", "Wild plants"),
                                   guide = "none"
                                   )


proj_season_order <- c("Cultivos_dry", "Cultivos_rainy", "Silvestres_dry", "Silvestres_rainy") 

proj_season_col <- c("#FFC107",  "#004D40", "#FFC107", "#004D40")

proj_season_symbol <- c(15, 16, 17, 18)

proj_season_shape <- scale_shape_manual(name = "Sampling",
                                   values = proj_season_symbol,
                                   limits = proj_season_order,
                                   labels = c("Fruit crops / Dry", "Fruit crops / Wet", "Wild plants / Dry", "Wild plants / Wet")
                                   )

proj_season_color <- scale_color_manual(name = "Season",
                                   values = proj_season_col,
                                   limits = proj_season_order,
                                   labels = c("Fruit crops / Dry", "Fruit crops / Wet", "Wild plants / Dry", "Wild plants / Wet")
                                   #guide = "right"
                                   )

proj_season_fill <- scale_fill_manual(name = "Season",
                                   values = proj_season_col,
                                   limits = proj_season_order,
                                   labels = c("Fruit crops / Dry", "Fruit crops / Wet", "Wild plants / Dry", "Wild plants / Wet")
                                   #guide = "none"
                                   )


crop_transect_order <- c( "Malus domestica", "Persea americana","Prunus domestica","Rubus", "Suria", "Tajo")

crop_transect_col <- c("#D55E00", "#009E73", "#F0E442", "#0072B2", "Black", "Grey60")


crop_transect_color <- scale_color_manual(name = "Fruit crop / Transect",
                                   values = crop_transect_col,
                                   limits = crop_transect_order,
                                   labels = c( "Malus domestica", "Persea americana","Prunus domestica","Rubus sp.", "Wild plants (Suria)", "Wild plants (Tajo)")
                                   #guide = "right"
                                   )
crop_transect_fill <- scale_fill_manual(name = "Fruitcrop",
                                   values = crop_transect_col,
                                   limits = crop_transect_order,
                                   guide = "none"
                                   )


```

# BETA DIVERSITY

Pairwise distance based on Hill numbers

The Sørensen‐type overlap (CqN for diversity) quantifies the effective average proportion of a subsystem (sampling unit) visitors that is shared across all sampling units. This is thus a metric that quantifies overlap from the subsystem (sampling units') perspective. 

The Jaccard‐type overlap (UqN) quantifies the effective proportion of visitors in a system (crop/transect) that are shared across all subsystem (sampling units). Hence, this metric quantifies overlap from the perspective of the overall system (crop/transect). 

The Sørensen‐type turnover‐complement (VqN) is the complement of the Sørensen‐type turnover, which quantifies the normalized visitor turnover rate with respect to the average subsystem (i.e., alpha), thus provides the proportion of a typical subsystem (sampling unit) that changes across subsystems.

The Jaccard‐type turnover‐complement (SqN) is the complement of the Jaccard‐type turnover, which quantifies the normalized visitor turnover rate with respect to the whole system (i.e. gamma).

Its corresponding dissimilarity eg. (1 − UqN) quantifies the effective proportion of nonshared visitors in the overall system.

Modified from: A guide to the application of Hill numbers to DNA‐based diversity analyses, Alberdi &Gilbert 2019 Mol Ecol Res

## Dissimilarity matrix project / season

Prepare data 

```{r pairwiseDistData, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}
table(bichos_long_filter$Proj_season, bichos_long_filter$Fruitcrop_transect)

# hierarchy
bichos_hier_df <- bichos_long_filter %>% 
				group_by(Sampling_unit, Proj_season, Project, Season) %>%
				dplyr::slice(1) %>% 
				select(Sampling_unit, Proj_season, Project, Season) %>%
				data.frame %>% 
				mutate(Sampling_unit = gsub("\\ ", ".", Sampling_unit),
					   Proj_season = gsub("\\ ", ".", Proj_season))

bichos_hier <- bichos_long_filter %>% 
				group_by(Sampling_unit, Proj_season) %>%
				dplyr::slice(1) %>% 
				select(Sampling_unit, Proj_season) %>%
				data.frame %>% 
				mutate(Sampling_unit = gsub("\\ ", ".", Sampling_unit),
					   Proj_season = gsub("\\ ", ".", Proj_season))
head(bichos_hier)

# format into a integer matrix
bichos_sampling <- bichos_long_filter %>% 
				group_by(Sampling_unit,  Lowest_assignment) %>%
				summarise(n_Lowest = n()) %>% data.frame

bichos_sampling$group <- paste(bichos_sampling$Proj_season, bichos_sampling$Sampling_unit, sep = ".")
head(bichos_sampling)

# Incidence matrix 

bichos_sampling <- bichos_long_filter %>%
				group_by(Sampling_unit,  Lowest_assignment) %>%
				summarise(n_Lowest = n()) %>% 
				mutate(n_Lowest = as.integer(ifelse(n_Lowest > 0, 1, 0))) 

# matrix
incidence_sampling <- bichos_sampling %>% 
			spread(Sampling_unit, n_Lowest, fill = 0) %>% data.frame

rownames(incidence_sampling) <- incidence_sampling[,1]

incidence_sampling <- incidence_sampling %>% select(-Lowest_assignment)

```

### Distance matrix (incidence data)

```{r distIncid, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

head(bichos_hier)
dist_q0 <- pair_dis(incidence_sampling, qvalue = 0)
dist_q1 <- pair_dis(incidence_sampling, qvalue = 1)
dist_q2 <- pair_dis(incidence_sampling, qvalue = 2)

sorensen_dist_q0 <- as.dist(dist_q0$L1_CqN)
sorensen_dist_q1 <- as.dist(dist_q1$L1_CqN)
sorensen_dist_q2 <- as.dist(dist_q2$L1_CqN)

#write.csv(sorensen_dist_q0, paste0(dataDir, "/Sorensen_Hill_distance.csv"))

```

Test whether the the grouping factor (Cultivos_dry vs. Cultivos_rainy vs. Silvestres_dry vs. Silvestres_rainy) has a
significant effect on overall insect visitor composition based on incidence data. 

```{r permanovaProjectSeason, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

set.seed(10112023)
incidence_permanova_q0 <- adonis2(t(sorensen_dist_q0) ~  Season + Project, data = bichos_hier_df, permutations=9999, na.rm = TRUE, by = "margin")

incidence_permanova_q0

incidence_permanova_q1 <- adonis2(t(sorensen_dist_q1) ~ Project + Season, data = bichos_hier_df, permutations=9999, na.rm = TRUE, by = "margin")
incidence_permanova_q1

incidence_permanova_q2 <- adonis2(t(sorensen_dist_q2) ~ Project + Season, data = bichos_hier_df, permutations=9999, na.rm = TRUE, by = "margin")
incidence_permanova_q2

# Calculate multivariate dispersions
project_dispersion <- betadisper(t(sorensen_dist_q1) , bichos_hier_df$Project)
season_dispersion <- betadisper(t(sorensen_dist_q1) , bichos_hier_df$Season)

plot(project_dispersion)
plot(season_dispersion)

# test for differences in dispersion 
anova(project_dispersion)
anova(season_dispersion)
     
# Permutation test for F
permutest(project_dispersion, pairwise = TRUE, permutations = 99)
permutest(season_dispersion, pairwise = TRUE, permutations = 99)
     
## Tukey's Honest Significant Differences
(proj_HSD <- TukeyHSD(project_dispersion))
(season_HSD <- TukeyHSD(season_dispersion))


```

>Insect visitor community composition is similar between projects and between seasons. Also, dispersion is similar between projects and seasons, so the assumption of similar multivariate spread among groups is not violated and differences are not confounded by differences in dispersion. 
>
Perform a NMDS 

```{r NMDSincid, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

# run NMDS q0
set.seed(20102023)
values_NMDS_q0 <- metaMDS(as.dist(sorensen_dist_q0), k = 4, trymax = 500)
values_NMDS_q0$stress

stressplot(values_NMDS_q0)

# run NMDS q1
set.seed(20102023)
values_NMDS_q1 <- metaMDS(as.dist(sorensen_dist_q1), k = 4, trymax = 500)
values_NMDS_q1$stress

stressplot(values_NMDS_q1)

# run NMDS q2
set.seed(20102023)
values_NMDS_q2 <- metaMDS(as.dist(sorensen_dist_q2), k = 4, trymax = 500)
values_NMDS_q2$stress

stressplot(values_NMDS_q2)

```

Get NMDS values for plot

```{r scoresNMDSincid, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

NMDS_scores_q0 <- data.frame(NMDS1 = values_NMDS_q0$point[, 1], NMDS2 = values_NMDS_q0$point[,2], NMDS3 = values_NMDS_q0$point[, 3], NMDS4 = values_NMDS_q0$point[, 4], Group = as.factor(bichos_hier[, 2]))
NMDS_centroids_q0 = aggregate(NMDS_scores_q0[, c(1:2)], by = list(NMDS_scores_q0[, 
            5]), FUN = mean)

NMDS_scores_q0$Sample <- rownames(NMDS_scores_q0)

colnames(NMDS_centroids_q0) <- c("Group", "x_cen", "y_cen")

NMDS_scores_q0 <- merge(NMDS_scores_q0, NMDS_centroids_q0, by = "Group")

NMDS_scores_q0 <- NMDS_scores_q0 %>% separate_wider_delim(Group, "_", names = c("Project", "Season") )

NMDS_scores_q0$Group <- paste(NMDS_scores_q0$Project, NMDS_scores_q0$Season, sep = "_")

NMDS_scores_q1 <- data.frame(NMDS1 = values_NMDS_q1$point[, 1], NMDS2 = values_NMDS_q1$point[,2], NMDS3 = values_NMDS_q1$point[, 3], NMDS4 = values_NMDS_q1$point[, 4], Group = as.factor(bichos_hier[, 2]))
NMDS_centroids_q1 = aggregate(NMDS_scores_q1[, c(1:2)], by = list(NMDS_scores_q1[, 
            5]), FUN = mean)

NMDS_scores_q1$Sample <- rownames(NMDS_scores_q1)

colnames(NMDS_centroids_q1) <- c("Group", "x_cen", "y_cen")

NMDS_scores_q1 <- merge(NMDS_scores_q1, NMDS_centroids_q1, by = "Group")

NMDS_scores_q1 <- NMDS_scores_q1 %>% separate_wider_delim(Group, "_", names = c("Project", "Season") )

NMDS_scores_q1$Group <- paste(NMDS_scores_q1$Project, NMDS_scores_q1$Season, sep = "_")

NMDS_scores_q2 <- data.frame(NMDS1 = values_NMDS_q2$point[, 1], NMDS2 = values_NMDS_q2$point[,2], NMDS3 = values_NMDS_q2$point[, 3], NMDS4 = values_NMDS_q2$point[, 4], Group = as.factor(bichos_hier[, 2]))

NMDS_centroids_q2 = aggregate(NMDS_scores_q2[, c(1:2)], by = list(NMDS_scores_q2[, 
            5]), FUN = mean)

NMDS_scores_q2$Sample <- rownames(NMDS_scores_q2)

colnames(NMDS_centroids_q2) <- c("Group", "x_cen", "y_cen")

NMDS_scores_q2 <- merge(NMDS_scores_q2, NMDS_centroids_q2, by = "Group")

NMDS_scores_q2 <- NMDS_scores_q2 %>% separate_wider_delim(Group, "_", names = c("Project", "Season") )
NMDS_scores_q2$Group <- paste(NMDS_scores_q2$Project, NMDS_scores_q2$Season, sep = "_")

```
Plot NMDS

```{r plotNMDSincid, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, fig.width = 10, fig.height = 5}

nmds_q0_proj_plot <- ggplot(NMDS_scores_q0, aes(x = NMDS1, y = NMDS2,colour = Season, fill = Season, shape = Project, linetype = Project)) + 
				geom_point(size = 2) + 
                season_color + 
                season_fill +
                project_shape +
                project_line +
        geom_point(data = NMDS_scores_q0, aes(x = x_cen, y = y_cen, fill = Season, shape = Project), colour = "black", size = 5, show.legend = FALSE) +
        ord_theme + theme(legend.text = element_text(face = "italic", size = 10), legend.title = element_text(size = 12))

nmds_q1_proj_plot <- ggplot(NMDS_scores_q1, aes(x = NMDS1, y = NMDS2, colour = Season, fill = Season, shape = Project, linetype = Project)) + 
				geom_point(size = 2) + 
                season_color + 
                season_fill +
                project_shape +
                project_line +
        geom_point(data = NMDS_scores_q1, aes(x = x_cen, y = y_cen, fill = Season, shape = Project), colour = "black", size = 5, show.legend = FALSE) +
        ord_theme + theme(legend.text = element_text(face = "italic", size = 10), legend.title = element_text(size = 12))
                
nmds_q2_proj_plot <- ggplot(NMDS_scores_q2, aes(x = NMDS1, y = NMDS2, colour = Season, fill = Season, shape = Project, linetype = Project)) + 
				geom_point(size = 2) + 
                season_color + 
                season_fill +
                project_shape +
                project_line +
        geom_point(data = NMDS_scores_q2, aes(x = x_cen, y = y_cen, fill = Season, shape = Project), colour = "black", size = 5, show.legend = FALSE) +
        ord_theme + theme(legend.text = element_text(face = "italic", size = 10), legend.title = element_text(size = 12))


# function for ellipsess 
veganCovEllipse <- function (cov, center = c(0, 0), scale = 1, npoints = 100) 
{
  theta <- (0:npoints) * 2 * pi/npoints
  Circle <- cbind(cos(theta), sin(theta))
  t(center + scale * t(Circle %*% chol(cov)))
}

# ellipses for q0 plot 

df_ell_q0 <- data.frame() #sets up a data frame before running the function.
for(g in levels(as.factor(NMDS_scores_q0$Group))){
  df_ell_q0 <- rbind(df_ell_q0, cbind(as.data.frame(with(NMDS_scores_q0 [NMDS_scores_q0$Group==g,],
 veganCovEllipse(cov.wt(cbind(NMDS1,NMDS2),wt=rep(1/length(NMDS1),length(NMDS1)))$cov,center=c(mean(NMDS1),mean(NMDS2))))) ,Group=g))
}

df_ell_q0 <- df_ell_q0 %>% separate_wider_delim(Group, "_", names = c("Project", "Season") )
df_ell_q0$Group <- paste(df_ell_q0$Project, df_ell_q0$Season, sep = "_")

# data for labelling the ellipse
NMDS_mean_q0 = aggregate(NMDS_scores_q0[ ,c("NMDS1", "NMDS2")], 
                         list(group = NMDS_scores_q0$Group), mean)

NMDS_mean_q0 <- NMDS_mean_q0 %>% separate_wider_delim(group, "_", names = c("Project", "Season") )
NMDS_mean_q0$Group <- paste(NMDS_mean_q0$Project, NMDS_mean_q0$Season, sep = "_")

# ellipses for q1 plot 

df_ell_q1 <- data.frame() #sets up a data frame before running the function.
for(g in levels(as.factor(NMDS_scores_q1$Group))){
  df_ell_q1 <- rbind(df_ell_q1, cbind(as.data.frame(with(NMDS_scores_q1 [NMDS_scores_q1$Group==g,],
 veganCovEllipse(cov.wt(cbind(NMDS1,NMDS2),wt=rep(1/length(NMDS1),length(NMDS1)))$cov,center=c(mean(NMDS1),mean(NMDS2))))) ,Group=g))
}


df_ell_q1 <- df_ell_q1 %>% separate_wider_delim(Group, "_", names = c("Project", "Season") )
df_ell_q1$Group <- paste(df_ell_q1$Project, df_ell_q1$Season, sep = "_")

# data for labelling the ellipse
NMDS_mean_q1 = aggregate(NMDS_scores_q1[ ,c("NMDS1", "NMDS2")], 
                         list(group = NMDS_scores_q1$Group), mean)

NMDS_mean_q1 <- NMDS_mean_q1 %>% separate_wider_delim(group, "_", names = c("Project", "Season") )
NMDS_mean_q1$Group <- paste(NMDS_mean_q1$Project, NMDS_mean_q1$Season, sep = "_")


# ellipses for q2 plot 

df_ell_q2 <- data.frame() #sets up a data frame before running the function.
for(g in levels(as.factor(NMDS_scores_q2$Group))){
  df_ell_q2 <- rbind(df_ell_q2, cbind(as.data.frame(with(NMDS_scores_q2 [NMDS_scores_q2$Group==g,],
 veganCovEllipse(cov.wt(cbind(NMDS1,NMDS2),wt=rep(1/length(NMDS1),length(NMDS1)))$cov,center=c(mean(NMDS1),mean(NMDS2))))) ,Group=g))
}

df_ell_q2 <- df_ell_q2 %>% separate_wider_delim(Group, "_", names = c("Project", "Season") )
df_ell_q2$Group <- paste(df_ell_q2$Project, df_ell_q2$Season, sep = "_")

# data for labelling the ellipse
NMDS_mean_q2 = aggregate(NMDS_scores_q2[ ,c("NMDS1", "NMDS2")], 
                         list(group = NMDS_scores_q2$Group), mean)

NMDS_mean_q2 <- NMDS_mean_q2 %>% separate_wider_delim(group, "_", names = c("Project", "Season") )
NMDS_mean_q2$Group <- paste(NMDS_mean_q2$Project, NMDS_mean_q2$Season, sep = "_")


nmds_q0_proj_plot <- nmds_q0_proj_plot + geom_path(data = df_ell_q0, aes(x = NMDS1, y = NMDS2, group = Group))

nmds_q1_proj_plot <- nmds_q1_proj_plot + geom_path(data = df_ell_q1, aes(x = NMDS1, y = NMDS2, group = Group))

nmds_q2_proj_plot <- nmds_q2_proj_plot + geom_path(data = df_ell_q2, aes(x = NMDS1, y = NMDS2, group = Group))
                
NMDS_proj_season <- ggarrange(nmds_q0_proj_plot, nmds_q1_proj_plot, nmds_q2_proj_plot, nrow = 1, labels = c("a.", "b.", "c."), font.label = c(size = 16), common.legend = TRUE, legend = "bottom")

png(paste0(outputDir, "/Figures/NMDS_proj_season.png"), width = 3000, height = 1500, res = 300) 
NMDS_proj_season
dev.off()
```



## Dissimilarity matrix fruitcrop_transect

Prepare data 

```{r pairwiseDistDataFruitcroptransect, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

str(bichos_long_filter)

# hierarchy
bichos_hier_df <- bichos_long_filter %>% 
				group_by(Sampling_unit, Project, Season, Fruitcrop_transect) %>%
				slice(1) %>% 
				select(Sampling_unit, Fruitcrop_transect) %>%
				data.frame %>% 
				mutate(Sampling_unit = gsub("\\ ", ".", Sampling_unit),
					   Fruitcrop_transect = gsub("\\ ", ".", Fruitcrop_transect))

# Incidence matrix 

bichos_sampling <- bichos_long_filter %>%
				group_by(Sampling_unit,  Lowest_assignment) %>%
				summarise(n_Lowest = n()) %>% 
				mutate(n_Lowest = as.integer(ifelse(n_Lowest > 0, 1, 0))) 

head(bichos_sampling)

# matrix
incidence_sampling <- bichos_sampling %>% 
			spread(Sampling_unit, n_Lowest, fill = 0) %>% data.frame

rownames(incidence_sampling) <- incidence_sampling[,1]

incidence_sampling <- incidence_sampling %>% select(-Lowest_assignment)

```

### Distance matrix (incidence data)

```{r distIncidFrTr, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

dist_q0 <- pair_dis(incidence_sampling, qvalue = 0)
dist_q1 <- pair_dis(incidence_sampling, qvalue = 1)
dist_q2 <- pair_dis(incidence_sampling, qvalue = 2)

sorensen_dist_q0 <- as.dist(dist_q0$L1_CqN)
sorensen_dist_q1 <- as.dist(dist_q1$L1_CqN)
sorensen_dist_q2 <- as.dist(dist_q2$L1_CqN)

#write.csv(sorensen_dist, paste0(dataDir, "/Sorensen_Hill_distance.csv"))

```

Test whether the there is a difference in composition among fruitcrops has a significant effect on overall insect visitor composition based on incidence data. 

```{r permanovaFrTr, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

set.seed(24102023)

incidence_permanova_q0 <- adonis2(t(sorensen_dist_q0) ~ Fruitcrop_transect, data = bichos_hier_df, permutations=9999, na.rm = TRUE)
incidence_permanova_q0

incidence_permanova_q1 <- adonis2(t(sorensen_dist_q1) ~ Fruitcrop_transect,
               data = bichos_hier_df, permutations=9999, na.rm = TRUE)
incidence_permanova_q1

incidence_permanova_q2 <- adonis2(t(sorensen_dist_q2) ~ Fruitcrop_transect,
               data = bichos_hier_df, permutations=9999, na.rm = TRUE)
incidence_permanova_q2

# Calculate multivariate dispersions
fruittran_dispersion <- betadisper(t(sorensen_dist_q1) , bichos_hier_df$Fruitcrop_transect)

plot(fruittran_dispersion)

# test for differences in dispersion 

anova(fruittran_dispersion)

# Permutation test for F
set.seed(231023)
permutest(fruittran_dispersion, pairwise = TRUE, permutations = 99)
     
## Tukey's Honest Significant Differences
fruittran_HSD <- TukeyHSD(fruittran_dispersion)
plot(fruittran_HSD)

```

>Insect visitor community composition is significantly different between fruitcrops and transect grouping, and the effect is similar across Hill numbers estimates (R2 = 0.10). Dispersion is similar between groups, so the assumption of similar multivariate spread among groups is not violated and differences are not confounded by differences in dispersion. Given that there is an issue of nestedness, it is not possible to model the effect of project, season, and fruitcrop / transect together.  
>
Perform a NMDS 

```{r NMDSincidFrTr, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

# run NMDS q0
set.seed(20102023)
values_NMDS_q0 <- metaMDS(as.dist(sorensen_dist_q0), k = 4, trymax = 500)
values_NMDS_q0$stress

stressplot(values_NMDS_q0)

# run NMDS q1
set.seed(20102023)
values_NMDS_q1 <- metaMDS(as.dist(sorensen_dist_q1), k = 4, trymax = 500)
values_NMDS_q1$stress

stressplot(values_NMDS_q1)

# run NMDS q2
set.seed(20102023)
values_NMDS_q2 <- metaMDS(as.dist(sorensen_dist_q2), k = 4, trymax = 500)
values_NMDS_q2$stress

stressplot(values_NMDS_q2)

```

NMDS values for plot

```{r scoresNMDSincidFrTr, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

NMDS_scores_q0 <- data.frame(NMDS1 = values_NMDS_q0$point[, 1], NMDS2 = values_NMDS_q0$point[,2], NMDS3 = values_NMDS_q0$point[, 3], NMDS4 = values_NMDS_q0$point[, 4], Group = as.factor(bichos_hier_df[, 4]))

NMDS_scores_q0 <- NMDS_scores_q0 %>% mutate(Group = gsub("\\.", " ", Group))


NMDS_centroids_q0 = aggregate(NMDS_scores_q0[, c(1:2)], by = list(NMDS_scores_q0[, 
            5]), FUN = mean)

NMDS_scores_q0$Sample <- rownames(NMDS_scores_q0)

colnames(NMDS_centroids_q0) <- c("Group", "x_cen", "y_cen")

NMDS_scores_q0 <- merge(NMDS_scores_q0, NMDS_centroids_q0, by = "Group")


NMDS_scores_q1 <- data.frame(NMDS1 = values_NMDS_q1$point[, 1], NMDS2 = values_NMDS_q1$point[,2], NMDS3 = values_NMDS_q1$point[, 3], NMDS4 = values_NMDS_q1$point[, 4], Group = as.factor(bichos_hier_df[, 4]))

NMDS_scores_q1 <- NMDS_scores_q1 %>% mutate(Group = gsub("\\.", " ", Group)) 

NMDS_centroids_q1 = aggregate(NMDS_scores_q1[, c(1:2)], by = list(NMDS_scores_q1[, 
            5]), FUN = mean)

NMDS_scores_q1$Sample <- rownames(NMDS_scores_q1)

colnames(NMDS_centroids_q1) <- c("Group", "x_cen", "y_cen")

NMDS_scores_q1 <- merge(NMDS_scores_q1, NMDS_centroids_q1, by = "Group")

NMDS_scores_q2 <- data.frame(NMDS1 = values_NMDS_q2$point[, 1], NMDS2 = values_NMDS_q2$point[,2], NMDS3 = values_NMDS_q2$point[, 3], NMDS4 = values_NMDS_q2$point[, 4], Group = as.factor(bichos_hier_df[, 4]))

NMDS_scores_q2 <- NMDS_scores_q2 %>% mutate(Group = gsub("\\.", " ", Group)) 

NMDS_centroids_q2 = aggregate(NMDS_scores_q2[, c(1:2)], by = list(NMDS_scores_q2[, 
            5]), FUN = mean)


NMDS_scores_q2$Sample <- rownames(NMDS_scores_q2)

colnames(NMDS_centroids_q2) <- c("Group", "x_cen", "y_cen")

NMDS_scores_q2 <- merge(NMDS_scores_q2, NMDS_centroids_q2, by = "Group")


```
Plot NMDS results using incidence data

```{r plotNMDSincidFrtr, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, fig.width = 10, fig.height = 5}

head(NMDS_scores_q0)

nmds_q0_fruitcrop_plot <- ggplot(NMDS_scores_q0, aes(x = NMDS1, y = NMDS2, colour = Group, fill = Group)) + 
				geom_point(size = 2) + 
         				crop_transect_color + 
                crop_transect_fill +
        geom_point(data = NMDS_scores_q0, aes(x = x_cen, y = y_cen, fill = Group), shape = 21,  colour = "black", size = 5, show.legend = FALSE) +
        ord_theme + theme(legend.text = element_text(face = "italic", size = 10), legend.title = element_text(size = 12))

nmds_q1_fruitcrop_plot <- ggplot(NMDS_scores_q1, aes(x = NMDS1, y = NMDS2, colour = Group, fill = Group)) + 
				geom_point(size = 2) + 
         				crop_transect_color + 
                crop_transect_fill +
        geom_point(data = NMDS_scores_q1, aes(x = x_cen, y = y_cen, fill = Group), shape = 21,  colour = "black", size = 5, show.legend = FALSE) +
        ord_theme + theme(legend.text = element_text(face = "italic", size = 10), legend.title = element_text(size = 12))

nmds_q2_fruitcrop_plot <- ggplot(NMDS_scores_q2, aes(x = NMDS1, y = NMDS2, colour = Group, fill = Group)) + 
				geom_point(size = 2) + 
         				crop_transect_color + 
                crop_transect_fill +
        geom_point(data = NMDS_scores_q2, aes(x = x_cen, y = y_cen, fill = Group), shape = 21,  colour = "black", size = 5, show.legend = FALSE) +
        ord_theme + theme(legend.text = element_text(face = "italic", size = 10), legend.title = element_text(size = 12))


# ellipses for q0 plot 
NMDS_scores_q0_noPrune <- NMDS_scores_q0 %>% filter(Group != "Prunus domestica")

#data for ellipse, in this case using the management factor
df_ell_q0 <- data.frame() #sets up a data frame before running the function.
for(g in levels(as.factor(NMDS_scores_q0_noPrune$Group))){
  df_ell_q0 <- rbind(df_ell_q0, cbind(as.data.frame(with(NMDS_scores_q0_noPrune [NMDS_scores_q0_noPrune$Group==g,],
 veganCovEllipse(cov.wt(cbind(NMDS1,NMDS2),wt=rep(1/length(NMDS1),length(NMDS1)))$cov,center=c(mean(NMDS1),mean(NMDS2))))) ,Group=g))
}
 
# data for labelling the ellipse
NMDS_mean_q0 = aggregate(NMDS_scores_q0_noPrune[ ,c("NMDS1", "NMDS2")], 
                         list(group = NMDS_scores_q0_noPrune$Group), mean)
 

# ellipses for q1 plot 
NMDS_scores_q1_noPrune <- NMDS_scores_q1 %>% filter(Group != "Prunus domestica")

#data for ellipse, in this case using the management factor
df_ell_q1 <- data.frame() #sets up a data frame before running the function.
for(g in levels(as.factor(NMDS_scores_q1_noPrune$Group))){
  df_ell_q1 <- rbind(df_ell_q1, cbind(as.data.frame(with(NMDS_scores_q1_noPrune [NMDS_scores_q1_noPrune$Group==g,],
 veganCovEllipse(cov.wt(cbind(NMDS1,NMDS2),wt=rep(1/length(NMDS1),length(NMDS1)))$cov,center=c(mean(NMDS1),mean(NMDS2))))) ,Group=g))
}
 
# data for labelling the ellipse
NMDS_mean_q1 = aggregate(NMDS_scores_q1_noPrune[ ,c("NMDS1", "NMDS2")], 
                         list(group = NMDS_scores_q1_noPrune$Group), mean)


# ellipses for q2 plot 
NMDS_scores_q2_noPrune <- NMDS_scores_q2 %>% filter(Group != "Prunus domestica")

#data for ellipse, in this case using the management factor
df_ell_q2 <- data.frame() #sets up a data frame before running the function.
for(g in levels(as.factor(NMDS_scores_q2_noPrune$Group))){
  df_ell_q2 <- rbind(df_ell_q2, cbind(as.data.frame(with(NMDS_scores_q2_noPrune [NMDS_scores_q2_noPrune$Group==g,],
 veganCovEllipse(cov.wt(cbind(NMDS1,NMDS2),wt=rep(1/length(NMDS1),length(NMDS1)))$cov,center=c(mean(NMDS1),mean(NMDS2))))) ,Group=g))
}
 
# data for labelling the ellipse
NMDS_mean_q2 = aggregate(NMDS_scores_q2_noPrune[ ,c("NMDS1", "NMDS2")], 
                         list(group = NMDS_scores_q2_noPrune$Group), mean)
 
nmds_q0_fruitcrop_plot <- nmds_q0_fruitcrop_plot + geom_path(data = df_ell_q0, aes(x = NMDS1, y = NMDS2, group = Group))

nmds_q1_fruitcrop_plot <- nmds_q1_fruitcrop_plot + geom_path(data = df_ell_q1, aes(x = NMDS1, y = NMDS2, group = Group))

nmds_q2_fruitcrop_plot <- nmds_q2_fruitcrop_plot + geom_path(data = df_ell_q2, aes(x = NMDS1, y = NMDS2, group = Group))

nmds_fruitcrop_plot <- ggarrange(nmds_q0_fruitcrop_plot, nmds_q1_fruitcrop_plot, nmds_q2_fruitcrop_plot, nrow = 1, labels = c("a.", "b.", "c."), font.label = c(size = 16), common.legend = TRUE, legend = "bottom")


png(paste0(outputDir, "/Figures/NMDS_fruitcrop_transect.png"), width = 3000, height = 1500, res = 300) 
nmds_fruitcrop_plot
dev.off()

```

Combine NMDS plots 

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

NMDS_combined <- ggarrange(nmds_q1_proj_plot, nmds_q1_fruitcrop_plot, nrow = 1, labels = c("a.", "b."), font.label = list(size = 20, face = "bold", family="Helvetica", size = 16), common.legend = FALSE, legend = "right")


png(paste0(outputDir, "/Figures/Figure2.png"), width = 3000, height = 1200, res = 300) 
NMDS_combined
dev.off()


```
```

# notes

```{r notes, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

# to get the polygons for a grouping factor
#Group_Tajo <- NMDS_scores[NMDS_scores$Group == "Tajo", ][chull(NMDS_scores[NMDS_scores$Group == "Tajo", c("NMDS1", "NMDS2")]),]

#bind hull data into object to add polygons to ggplot

#geom_polygon(data = hull_data, aes(x = NMDS1, y = NMDS2), alpha = 0.5) +
```

## Session Info

```{r sessionInfo, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}
sessioninfo::session_info()%>%
  details::details(summary = 'Current session info', open = FALSE)
```



