---
title: 'Exploration alpha diversity of insect visitors'
author: "B. Karina Montero "
date: "`r Sys.Date()`"
output: html_document
---


### LOAD LIBRARIES

```{r libraries, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

rm(list = ls())

# basics

library(tidyverse)
library(stringr)
library(vegan)
library(magrittr)

# graphics
library(ggplot2)
library(ggpubr)
library(ggVennDiagram)
library(grid)
library(png)
library(cowplot)
library(magick)
library(gtable)

# diversity 
library(iNEXT)
library(hilldiv)

# rmd
library(details)
library(knitr)
library(kableExtra)

```

### WORKING DIRECTORIES

```{r source, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

source("/home/kari/Dropbox/PollenUCR/01_scripts/UCR_workingDirectories.R")
source("/home/kari/Dropbox/REPO/PollenMetabarcoding/pollen_graphics_param.R")
```


### LOAD DATA

```{r metadata, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

bichos_long_filter <- read.csv(paste0(dataDir, "/bichos_long_filter.csv"))

(sample_size_project <- bichos_long_filter %>%
 							group_by(Project) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit))) 
(sample_size_proj_season <- bichos_long_filter %>%
 							group_by(Proj_season) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit))) 
(sample_size_crop <- bichos_long_filter %>%
							filter(Project == "Cultivos") %>%
 							group_by(Plant_species) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit))) 
(sample_size_farm <- bichos_long_filter %>%
 							group_by(Proj_site, Farm_transect) %>% 
 							summarise(n_sampling = n_distinct(Sampling_unit))) 
```


# ALPHA DIVERSITY

## Is insect visitor alpha diversity different between fruit crops and native plants across seasons?

Prepare incidence data 

```{r projSeasoniNextData, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, results = "hide"}

# Incidence_raw = species-by-sampling-unit matrix 

bichos_long_filter$Sampling_unit <- paste("Gira", bichos_long_filter$Sampling_session, bichos_long_filter$Fruitcrop_transect, bichos_long_filter$Day, bichos_long_filter$Month, sep = "_")

bichos_sampling <- bichos_long_filter %>%
				group_by(Proj_season, Sampling_unit,  Lowest_assignment) %>%
				summarise(n_Lowest = n()) %>% 
				mutate(n_Lowest = as.integer(ifelse(n_Lowest > 0, 1, 0)) )
head(bichos_sampling, 3)

# format cultivos dry into a integer matrix
incidence_cultivos_dry <- bichos_sampling %>% 
					filter(Proj_season == "Cultivos_dry") %>% 
					group_by(Sampling_unit) %>%
					spread(Sampling_unit, n_Lowest, fill = 0) %>% select(-Proj_season) %>%
					data.frame
str(incidence_cultivos_dry)

incidence_cultivos_dry <- as.matrix(apply(incidence_cultivos_dry[,-1],2,as.integer))
rownames(incidence_cultivos_dry) <- incidence_cultivos_dry[,1]

# format cultivos rainy into a integer matrix
incidence_cultivos_rainy <- bichos_sampling %>% 
					filter(Proj_season == "Cultivos_rainy") %>% 
					group_by(Sampling_unit) %>%
					spread(Sampling_unit, n_Lowest, fill = 0) %>% select(-Proj_season) %>%
					data.frame
str(incidence_cultivos_rainy)

incidence_cultivos_rainy <- as.matrix(apply(incidence_cultivos_rainy[,-1],2,as.integer))
rownames(incidence_cultivos_rainy) <- incidence_cultivos_rainy[,1]

# format silvestres dry into a integer matrix
incidence_silvestres_dry <- bichos_sampling %>% 
					filter(Proj_season == "Silvestres_dry") %>% 
					group_by(Sampling_unit) %>%
					spread(Sampling_unit, n_Lowest, fill = 0) %>% select(-Proj_season) 
incidence_silvestres_dry <- as.matrix(apply(incidence_silvestres_dry[,-1],2,as.integer))

rownames(incidence_silvestres_dry) <- incidence_silvestres_dry[,1]
str(incidence_silvestres_dry)

# format silvestres rainy into a integer matrix
incidence_silvestres_rainy <- bichos_sampling %>% 
					filter(Proj_season == "Silvestres_rainy") %>% 
					group_by(Sampling_unit) %>%
					spread(Sampling_unit, n_Lowest, fill = 0) %>% select(-Proj_season) 
incidence_silvestres_rainy <- as.matrix(apply(incidence_silvestres_rainy[,-1],2,as.integer))
rownames(incidence_silvestres_rainy) <- incidence_silvestres_rainy[,1]
str(incidence_silvestres_rainy)

# create a list 
incidence_bichos <- list(Cultivos_dry = incidence_cultivos_dry, Cultivos_rainy = incidence_cultivos_rainy, Silvestres_dry = incidence_silvestres_dry, Silvestres_rainy = incidence_silvestres_rainy)
str(incidence_bichos)

```
Venn of shared taxonomy (lower_assignment)

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, eval= FALSE}

cultivos_rainy <- bichos_sampling %>% 
					filter(Proj_season == "Cultivos_rainy") %>%
					group_by(Lowest_assignment) %>%
					select(Lowest_assignment) %>% 
					slice(1) %>%
					data.frame
cultivos_dry <- bichos_sampling %>% 
					filter(Proj_season == "Cultivos_dry") %>%
					group_by(Lowest_assignment) %>%
					select(Lowest_assignment) %>% 
					slice(1) %>%
					data.frame 
silvestres_rainy <- bichos_sampling %>% 
					filter(Proj_season == "Silvestres_rainy") %>%
					group_by(Lowest_assignment) %>%
					select(Lowest_assignment) %>% 
					slice(1) %>%
					data.frame 
silvestres_dry <- bichos_sampling %>% 
					filter(Proj_season == "Silvestres_dry") %>%
					group_by(Lowest_assignment) %>%
					select(Lowest_assignment) %>% 
					slice(1) %>%
					data.frame 
list_all <- list(silvestres_dry = silvestres_dry[,1], cultivos_dry = cultivos_dry[,1], silvestres_rainy = silvestres_rainy[, 1], cultivos_rainy = cultivos_rainy[,1])
str(list_all)

# construct a Venn object
venn = Venn(list_all)
data = process_data(venn, shape_id = "401f")
str(data)
data_mod <- venn_region(data) %>%
		mutate(percent = scales::percent(round(venn_region(data)$count/sum(venn_region(data)$count),3))) 

venn_visitors <- ggplot() +
  geom_sf(aes(fill = count), data = venn_region(data)) +
  geom_sf(color = "grey20", data = venn_setedge(data), show.legend = FALSE) +
  geom_sf_text(label = c("Wild plants \n Dry", "Fruit crops \n Dry", "Wild plants \n Wet", "Fruit crops \n Wet"), data = venn_setlabel(data), size = 3.1) +
  geom_sf_label(aes(label = paste0(count, "(", percent, ")")),
  		data = data_mod, alpha = 0.6, size = 2.8)+
  theme_void() +
  scale_fill_distiller(name = "n Taxa", palette = "PiYG", breaks = c(20, 60, 100, 140)) + 
  scale_x_continuous(expand = expansion(mult = .2))+ 
  theme(legend.position = "bottom",
  		legend.key.size = unit(0.5, 'cm'), 
  		legend.title = element_text(size = 10), 
  		legend.text = element_text(size = 9))

#png(paste0(outputDir, "/Figures/venn_visitors.png"), width = 3000, height = 2800, res = 250) 
venn_visitors
#dev.off()

```

Run iNEXT on incidence data

```{r projSeasonIncid, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

inext_visitors <- iNEXT(incidence_bichos, q = c(0, 1, 2), datatype = "incidence_raw")

DataInfo(incidence_bichos, "incidence_raw")
```

Completeness curve 

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

#Sample completeness curve (type=2) with confidence intervals (if se=TRUE): see Figs. 1b and 2b in Hsieh et al. (2016). This curve plots the sample coverage with respect to sample size for the same range described in (1).

proj_season_compl_curve <- ggiNEXT(inext_visitors, type = 2)

proj_season_compl_curve_p <- proj_season_compl_curve + 
					proj_season_color +
					proj_season_fill + 
					pca_theme + 
					annotate(geom = "text", x = 7, y= 0.56, 
						label = "Fruit crops, Dry season (56%)", hjust = -.2) +
					annotate(geom = "text", x = 10, y= 0.70, 
						label = "Wild plants, Dry season (70%)", hjust = -.2) +
					annotate(geom = "text", x = 22, y= 0.83, 
						label = "Wild plants, Rainy season (83%)", hjust = -.2) +
					annotate(geom = "text", x = 28, y= 0.85, 
						label = "Fruit crops, Rainy season (85%)", hjust = -.2) +
					theme_set(theme_bw(base_size = 14)) + 
					theme(legend.position = "none", axis.line = element_line(colour = "black"),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border=element_blank(),plot.margin=grid::unit(c(5,5,5,5), "mm"), axis.text.x = element_text(colour = "black", size=rel(1)), axis.text.y=element_text(size=rel(1), colour="black"), axis.title = element_text(size = rel(1)))
proj_season_compl_curve_p 
 

#png(paste0(outputDir, "/Figures/proj_season_completeness_curve.png"), width = 2700, height = 1700, res = 250) 
proj_season_compl_curve_p 
#dev.off()
 	
```

Coverage-based curve 

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

# Coverage-based R/E curve (type=3): see Figs. 1c and 2c in Hsieh et al. (2016). This curve plots the diversity estimates with confidence intervals (if se=TRUE) as a function of sample coverage up to the maximum coverage obtained from the maximum size described in (1)

proj_season_coverage_curve <- ggiNEXT(inext_visitors, type = 3, facet.var = "Order.q")

proj_season_coverage_curve_p <- proj_season_coverage_curve + 
					proj_season_color +
					proj_season_fill + 
					proj_season_shape +
					pca_theme + 
					theme_set(theme_bw(base_size = 14)) + 
					theme( axis.line = element_line(colour = "black"),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border=element_blank(),plot.margin=grid::unit(c(5,5,5,5), "mm"), axis.text.x = element_text(colour = "black", size=rel(1)), axis.text.y=element_text(size=rel(1), colour="black"), axis.title = element_text(size = rel(1)))

proj_season_coverage_curve_p

#png(paste0(outputDir, "/Figures/proj_season_RE_curve.png"), width = 3000, height = 1700, res = 250) 
proj_season_coverage_curve_p 
#dev.off()

```

> The coverage for incidence data is lower than that of abundance data. Fruitcrops during the dry season has the lowest coverage, 56%, with a reference sample size of 7 sampling units, is followed by the wild plant transects with an estimated coverage of 71% with a reference sample size of 11 sampling units. This means that 44% of individuals sampled in the dry season in fruitcrops belong to species missed during fieldwork.  The coverage during the rainy season is similar for both fruitcrops and wild plant transects, estimates as 86% and 84% with a reference sample size of 36 and 26 sampling units respectively. 
> 

Hill numbers estimates (coverageD)

```{r projSeasonCoverage, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

coverage_incidence <- estimateD(incidence_bichos, q = c(0, 1, 2), datatype = "incidence_raw", base = "coverage", conf = 0.95)

coverage_incidence$ID <- paste("Incidence", coverage_incidence$Assemblage, coverage_incidence$Order.q, sep = "_")

coverage_incidence_long <- coverage_incidence %>%
						select(-Assemblage, -Order.q, -t, - Method, -SC) %>%
						pivot_longer(!ID, 
									names_to = "iNEXT_est", 
									values_to = "estimate")

coverage_incidence_long <- coverage_incidence_long %>% separate_wider_delim(cols = ID, delim = "_", names = c("Data_type", "Project", "Season", "Hill_number"))
```


PLot Incidence Data (coverage)

```{r projSeasonIncidCoveragePlots, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE,  fig.show="hide"}

season_names <- c('dry' = "Dry", 'rainy' = "Wet" )

(richness_coverage_p <- coverage_incidence_long %>% 
				filter(Hill_number == "0", Data_type == "Incidence") %>% 
				pivot_wider(names_from = "iNEXT_est", values_from = "estimate") %>%
				ggplot(aes(x = Project, y = qD, group=1)) +
	  				 geom_errorbar(width=.1, aes(ymin = qD.LCL, ymax = qD.UCL)) +
	  				 geom_point(shape=21, size=4, fill="grey") +
	  				 facet_grid(~Season, labeller = as_labeller(season_names)) + 
	  				 scale_x_discrete(labels=c('Cultivos' = "Fruit crops", 'Silvestres' = "Wild plants")) +
	  				 xlab("") + ylab("Richness") +
	  				 div_theme + 
	  				 theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)))

(shannon_coverage_p <- coverage_incidence_long %>% 
				filter(Hill_number == "1", Data_type == "Incidence") %>% 
				pivot_wider(names_from = "iNEXT_est", values_from = "estimate") %>%
				ggplot(aes(x = Project, y = qD, group=1)) +
	  				 geom_errorbar(width=.1, aes(ymin = qD.LCL, ymax = qD.UCL)) +
	  				geom_point(shape=21, size=4, fill="grey") +
	  				 facet_grid(~Season, labeller = as_labeller(season_names)) + 
	  				 scale_x_discrete(labels=c('Cultivos' = "Fruit crops", 'Silvestres' = "Wild plants")) +
	  				 xlab("") + ylab("Hill-Shannon") +
	  				 div_theme + 
	  				 theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)))

(simpson_coverage_p <- coverage_incidence_long %>% 
				filter(Hill_number == "2", Data_type == "Incidence") %>% 
				pivot_wider(names_from = "iNEXT_est", values_from = "estimate") %>%
				ggplot(aes(x = Project, y = qD, group=1)) +
	  				 geom_errorbar(width=.1, aes(ymin = qD.LCL, ymax = qD.UCL)) +
	  				 geom_point(shape=21, size=4, fill="grey") +
	  				 facet_grid(~Season, labeller = as_labeller(season_names)) + 
	  				 scale_x_discrete(labels=c('Cultivos' = "Fruit crops", 'Silvestres' = "Wild plants")) +
	  				 xlab("") + ylab("Hill-Simpson") +
	  				 div_theme + 
	  				 theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)))

#alpha_visitors_p <- ggarrange(richness_coverage_p, shannon_coverage_p, simpson_coverage_p, nrow = 1, labels = c("a)", "b)", "c)"), font.label = list(size = 16, face = "bold"))

alpha_visitors_p <- ggarrange(richness_coverage_p, shannon_coverage_p, simpson_coverage_p, nrow = 1)

#png(paste0(outputDir, "/Figures/alpha_visitors_proj_season.png"), width = 3000, height = 1200, res = 300) 
alpha_visitors_p
#dev.off()

```

## Within fruit crop diversity

### Is insect visitor alpha diversity different across fruit crops?

```{r cultivosiNextData, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, results = "hide"}

#1. incidence_raw = species-by-sampling-unit matrix 

bichos_long_filter$Sampling_unit <- paste("Gira", bichos_long_filter$Sampling_session, bichos_long_filter$Fruitcrop_transect, bichos_long_filter$Day, bichos_long_filter$Month, sep = "_")

bichos_sampling <- bichos_long_filter %>%
				filter(Project == "Cultivos") %>%
				group_by(Plant_species , Sampling_unit,  Lowest_assignment) %>%
				summarise(n_Lowest = n()) %>% 
				mutate(n_Lowest = as.integer(ifelse(n_Lowest > 0, 1, 0)) )
head(bichos_sampling)
tail(bichos_sampling)
table(bichos_sampling$Plant_species)

# format Malus into a integer matrix
incidence_malus <- bichos_sampling %>%
					filter(Plant_species == "Malus domestica") %>%	 
					group_by(Sampling_unit) %>%
					spread(Sampling_unit, n_Lowest, fill = 0) %>% select(-Plant_species) %>%
					data.frame
str(incidence_malus)
incidence_malus <- as.matrix(apply(incidence_malus[,-1],2,as.integer))
rownames(incidence_malus) <- incidence_malus[,1]

# format Persea into a integer matrix
incidence_persea <- bichos_sampling %>%
					filter(Plant_species == "Persea americana") %>%	 
					group_by(Sampling_unit) %>%
					spread(Sampling_unit, n_Lowest, fill = 0) %>% select(-Plant_species) %>%
					data.frame
str(incidence_persea)
incidence_persea <- as.matrix(apply(incidence_persea[,-1],2,as.integer))
rownames(incidence_persea) <- incidence_persea[,1]

# format Prunus into a integer matrix
incidence_prunus <- bichos_sampling %>%
					filter(Plant_species == "Prunus domestica") %>%	 
					group_by(Sampling_unit) %>%
					spread(Sampling_unit, n_Lowest, fill = 0) %>% select(-Plant_species) %>%
					data.frame
str(incidence_prunus)
incidence_prunus <- as.matrix(apply(incidence_prunus[,-1],2,as.integer))
rownames(incidence_prunus) <- incidence_prunus[,1]

# format Rubus into a integer matrix
incidence_rubus <- bichos_sampling %>%
					filter(Plant_species == "Rubus") %>%	 
					group_by(Sampling_unit) %>%
					spread(Sampling_unit, n_Lowest, fill = 0) %>% select(-Plant_species) %>%
					data.frame
str(incidence_rubus)
incidence_rubus <- as.matrix(apply(incidence_rubus[,-1],2,as.integer))
rownames(incidence_rubus) <- incidence_rubus[,1]

# create a list 
incidence_bichos <- list(Malus = incidence_malus, Persea = incidence_persea, Prunus = incidence_prunus, Rubus = incidence_rubus)
str(incidence_bichos)

```


iNEXT on within fruit crop incidence data 

```{r inextCultivosIncid, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

inext_visitors <- iNEXT(incidence_bichos, q = c(0, 1, 2), datatype = "incidence_raw")

inext_visitors$DataInfo

coverage_incidence <- estimateD(incidence_bichos, q = c(0, 1, 2), datatype = "incidence_raw", base = "coverage", conf = 0.95)

```

Completeness curve 

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

#Sample completeness curve (type=2) with confidence intervals (if se=TRUE): see Figs. 1b and 2b in Hsieh et al. (2016). This curve plots the sample coverage with respect to sample size for the same range described in (1).

fruitcrop_compl_curve <- ggiNEXT(inext_visitors, type = 2)

labels <- data.frame(
  x = c(4, 3, 8, 20), 
  y = c(0.45, 0.45, 0.68, 0.86), 
  label = c("()", "()", "()", "()")
)

fruitcrop_compl_curve_p <- fruitcrop_compl_curve + 
					crop_color +
					crop_fill + 
					pca_theme + 
					annotate(geom = "text", x = 4, y= 0.45, 
						label = "Malus domestica (45%)", hjust = -.2) +
					annotate(geom = "text", x = 2, y= 0.50, 
						label = "Prunus domestica (45%)", hjust = -.2) +
					annotate(geom = "text", x = 8, y= 0.68, 
						label = "Rubus (68%)", hjust = -.2) +
					annotate(geom = "text", x = 20, y= 0.86, 
						label = "Persea americana (86%)", hjust = -.2) +
					theme_set(theme_bw(base_size = 14)) + 
					theme(legend.position = "none", axis.line = element_line(colour = "black"),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border=element_blank(),plot.margin=grid::unit(c(5,5,5,5), "mm"), axis.text.x = element_text(colour = "black", size=rel(1)), axis.text.y=element_text(size=rel(1), colour="black"), axis.title = element_text(size = rel(1)))
fruitcrop_compl_curve_p 

png(paste0(outputDir, "/Figures/fruitcrop_completeness_curve.png"), width = 2700, height = 1700, res = 250) 
fruitcrop_compl_curve_p 
dev.off()
 	
```

>Sample coverage is lowest for Prunus (40%), followed by Malus (62%), Rubus (68%) and Persea (86%) with reference sample sizes od 6, 9, 8 and 20 sampling units respectively. 


Coverage-based curve 

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

# Coverage-based R/E curve (type=3): see Figs. 1c and 2c in Hsieh et al. (2016). This curve plots the diversity estimates with confidence intervals (if se=TRUE) as a function of sample coverage up to the maximum coverage obtained from the maximum size described in (1)

fruitcrop_coverage_curve <- ggiNEXT(inext_visitors, type = 3, facet.var = "Order.q")

fruitcrop_coverage_curve_p <- fruitcrop_coverage_curve + 
					crop_color +
					crop_fill + 
					pca_theme + 
					theme_set(theme_bw(base_size = 14)) + 
					theme( axis.line = element_line(colour = "black"),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border=element_blank(),plot.margin=grid::unit(c(5,5,5,5), "mm"), axis.text.x = element_text(colour = "black", size=rel(1)), axis.text.y=element_text(size=rel(1), colour="black"), axis.title = element_text(size = rel(1)))

fruitcrop_coverage_curve_p

png(paste0(outputDir, "/Figures/fruitcrop_RE_curve.png"), width = 3000, height = 1700, res = 250) 
fruitcrop_coverage_curve_p 
dev.off()

```

Within crops Hill numbers estimates (coverageD)

```{r cultivosAbundCoverage, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}

coverage_incidence$ID <- paste("Incidence", coverage_incidence$Assemblage, coverage_incidence$Order.q, sep = "_")

coverage_incidence_long <- coverage_incidence %>%
						select(-Assemblage, -Order.q, -t, - Method, -SC) %>%
						pivot_longer(!ID, 
									names_to = "iNEXT_est", 
									values_to = "estimate")


coverage_incidence_long <- coverage_incidence_long %>% separate_wider_delim(cols = ID, delim = "_", names = c("Data_type", "Project", "Hill_number"))
str(coverage_incidence_long)

```

Plot coverage-based Hill diversity

```{r CropsIncidCoveragePlots, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE,  fig.show="hide"}

(richness_coverage_p <- coverage_incidence_long %>% 
			filter(Hill_number == "0", Data_type == "Incidence") %>% 
			pivot_wider(names_from = "iNEXT_est", values_from = "estimate") %>%
			ggplot(aes(x = Project, y = qD, group=1)) +
  				 geom_errorbar(width=.1, aes(ymin = qD.LCL, ymax = qD.UCL)) +
  				 geom_point(shape=21, size=4, fill="grey")+
  				 xlab("") + ylab("Richness") +
  				 div_theme + 
	  			theme(axis.text.x = element_text(face = "italic", angle = 45, vjust = 0.9, hjust=1)))

(shannon_coverage_p <- coverage_incidence_long %>% 
			filter(Hill_number == "1", Data_type == "Incidence") %>% 
			pivot_wider(names_from = "iNEXT_est", values_from = "estimate") %>%
			ggplot(aes(x = Project, y = qD, group=1)) +
  				 geom_errorbar(width=.1, aes(ymin = qD.LCL, ymax = qD.UCL)) +
  				 geom_point(shape=21, size=4, fill="grey")+
  				 xlab("") + ylab("Hill-Shannon") +
  				 div_theme + 
	  			theme(axis.text.x = element_text(face = "italic", angle = 45, vjust = 0.9, hjust=1)))

(simpson_coverage_p <- coverage_incidence_long %>% 
			filter(Hill_number == "2", Data_type == "Incidence") %>% 
			pivot_wider(names_from = "iNEXT_est", values_from = "estimate") %>%
			ggplot(aes(x = Project, y = qD, group=1)) +
  				 geom_errorbar(width=.1, aes(ymin = qD.LCL, ymax = qD.UCL)) +
  				 geom_point(shape=21, size=4, fill="grey")+
  				 xlab("") + ylab("Hill-Simpson") +
  				 div_theme + 
	  			theme(axis.text.x = element_text(face = "italic", angle = 45, vjust = 0.9, hjust=1)))

alpha_fruitcrops_p <- ggarrange(richness_coverage_p, shannon_coverage_p, simpson_coverage_p, nrow = 1)

```


Figure 1

```{r, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE, eval = FALSE}


# Get image
img_path <- "/home/kari/Dropbox/PollenUCR/07_Fotos/"
img <- readPNG(paste0(img_path,"SanGerardo.png"))
g <- rasterGrob(img, interpolate=TRUE, width = unit(3,"in"), height=unit(3,"in"))
img_p <- ggdraw() + draw_image(img)


png(paste0(outputDir, "/Figures/Figure1.png"), width = 3000, height = 2800, res = 300) 

pushViewport(viewport(layout  =  grid.layout(26, 12)))
vplayout <- function(x, y) viewport(layout.pos.row  =  x, layout.pos.col  =  y)

print(img_p + theme(plot.title = element_text(size = 20, hjust=0.01, vjust = -3.0, face = "bold",family="Helvetica"))+ggtitle("a."), vp = vplayout(1:9, 1:6))

print(venn_visitors + theme(legend.position = "none", plot.title = element_text(size = 20, hjust=0.01, vjust = -3.0, face = "bold",family="Helvetica"))+ggtitle("b."), vp = vplayout(1:10, 7:12))

legend = gtable_filter(ggplotGrob(venn_visitors), "guide-box")
legend$vp = viewport(layout.pos.row = 9, layout.pos.col = 11:12)
grid.draw(legend)

print(alpha_visitors_p + theme(plot.title = element_text(size = 20,hjust=0.01, vjust = -3, face = "bold",family="Helvetica")) + ggtitle("c."), vp = vplayout(10:18,1:12))

print(alpha_fruitcrops_p + theme(plot.title = element_text(size = 20,hjust=0.01, vjust = -3, face = "bold",family="Helvetica")) + ggtitle("d."), vp = vplayout(18:26,1:12))
dev.off()

```



## Session Info

```{r sessionInfo, message=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=45), paged.print=FALSE}
sessioninfo::session_info()%>%
  details::details(summary = 'Current session info', open = FALSE)
```